Modelling BCG vaccination in the UK

### 2019-08-06 rmds/06-tb-bcg-improv-outcomes.Rmd
edits through to chapter 7

sum_imp_ageatvac %>% 
  set_names( c('Outcome', 'Age group', 'OR (95\\% CI)', 'P-value', 'fmi', 'aOR (95\\% CI)', 'P-value', 'fmi')) %>% 
  imp_tab_gen(caption = 'Summary of associations between age at vaccination and all outcomes, using pooled imputed data (reference is vaccination at <1 year).', escape = FALSE) %>% 
  add_header_above(c(" " = 2, "Univariable" = 3, "Multivariable" = 3))
```

@@

```{r 06-sens-table, message=FALSE, echo=FALSE, results='asis', warning=FALSE}
bcg_ass_main %>% 
  set_names(c('Study population', 'Outcome', 'BCG', 'OR (95% CI)', 'P-value', 'aOR (95% CI)', 'P-value')) %>% 
  kable(
    caption.short = "Summary of associations between BCG vaccination and all outcomes.", 
    caption = "Summary of associations between BCG vaccination and all outcomes; cases that have no recurrent flag in the ETS (n=50407), and cases that would have been eligible for the BCG schools scheme (n=9943). Those defined to be eligible for the schools scheme are the UK born, that were aged 14 or over in 2004", booktabs = TRUE) %>% 
    column_spec(c(1:2), width = "3cm") %>% 
    kable_styling(latex_options = "HOLD_position") %>%
    add_footnote(label = c("OR: odds ratio with 95% confidence intervals", "aOR: adjusted odds ratio with 95% confidence intervals",
                         "fmi: fraction of missing information",
                         "* Death due to TB in those who died and where cause of death was known"),
               notation = "none") %>% 
    add_header_above(c(" " = 3, "Univariable" = 2, "Multivariable" = 2)) 
```

>>>>

sum_imp_ageatvac %>% 
  set_names( c('Outcome', 'Age group', 'OR (95\\% CI)', 'P-value', 'fmi', 'aOR (95\\% CI)', 'P-value', 'fmi')) %>% 
  imp_tab_gen(caption = 'Summary of associations between age at vaccination and all outcomes, using pooled imputed data (reference is vaccination at <1 year).', escape = FALSE) %>% 
  add_header_above(c(" " = 2, "Univariable" = 3, "Multivariable" = 3)) %>% 
  kable_styling(font_size = 8)
```

@@

```{r 06-sens-table, message=FALSE, echo=FALSE, results='asis', warning=FALSE}
bcg_ass_main %>% 
  set_names(c('Study population', 'Outcome', 'BCG', 'OR (95% CI)', 'P-value', 'aOR (95% CI)', 'P-value')) %>% 
  kable(
    caption.short = "Summary of associations between BCG vaccination and all outcomes.", 
    caption = "Summary of associations between BCG vaccination and all outcomes; cases that have no recurrent flag in the ETS (n=50407), and cases that would have been eligible for the BCG schools scheme (n=9943). Those defined to be eligible for the schools scheme are the UK born, that were aged 14 or over in 2004", booktabs = TRUE) %>% 
    column_spec(c(1:2), width = "3cm") %>% 
    kable_styling(font_size = 8, latex_options = "HOLD_position") %>%
    add_footnote(label = c("OR: odds ratio with 95% confidence intervals", "aOR: adjusted odds ratio with 95% confidence intervals",
                         "fmi: fraction of missing information",
                         "* Death due to TB in those who died and where cause of death was known"),
               notation = "none") %>% 
    add_header_above(c(" " = 3, "Univariable" = 2, "Multivariable" = 2)) 
```
